---
title: "GoGo Camp #1 Assessment Analysis"
format: html
execute:
  message: false
  warning: false
editor: visual
---

This is our analysis for camp #1.

We have two over-arching goals that would correspond to different analyses:

HIGHEST LEVEL GOAL - 

Leah works on framing, Cody works on collecting, Josh works on visualizing, with achieving this goal top of mind:

1. Understand the response patterns to gauge how well the items are working in terms of our goal of understanding youth learning:
- Descriptives, in aggregate, pre-post:
- Recode the data
- Have clear labels for what the different response options mean
- Keep the same scale, but have clear labels

---

2. Understand changes in learning that can be attributed to the camp
- In aggregate (i.e., sum or mean or other summary statistic), pre-post, may want to share some measure of variation (SD, SE, individual student data) around the aggregate statistic

```{r}
library(tidyverse) # install.packages("tidyverse")
library(googlesheets4) # install.packages("googlesheets4")

start_1 <- read_sheet("https://docs.google.com/spreadsheets/d/1olSCB0OeuG1Ysqbj-0SYkZnskJkTNhi0BWI8_sONWe0/edit#gid=1481701584", sheet = 1, n_max = 21)
start_2 <- read_sheet("https://docs.google.com/spreadsheets/d/1olSCB0OeuG1Ysqbj-0SYkZnskJkTNhi0BWI8_sONWe0/edit#gid=1481701584", sheet = 2, n_max = 17)
start_3 <- read_sheet("https://docs.google.com/spreadsheets/d/1olSCB0OeuG1Ysqbj-0SYkZnskJkTNhi0BWI8_sONWe0/edit#gid=1481701584", sheet = 3, n_max = 18)

pseudonyms <- read_sheet("https://docs.google.com/spreadsheets/d/1UAXIhQFD_JYTWKuC9mZrLGmfBCNYRpcpkmIkZIrheIM/edit#gid=0")
  
end_1 <- read_sheet("https://docs.google.com/spreadsheets/d/1RIBfcVUh5B0wA_jzGHVbPlSezVJWcuCekqWa2zSgnqw/edit#gid=429607552", sheet = 1, n_max = 24)
end_2 <- read_sheet("https://docs.google.com/spreadsheets/d/1RIBfcVUh5B0wA_jzGHVbPlSezVJWcuCekqWa2zSgnqw/edit#gid=429607552", sheet = 2, n_max = 25)
end_3 <- read_sheet("https://docs.google.com/spreadsheets/d/1RIBfcVUh5B0wA_jzGHVbPlSezVJWcuCekqWa2zSgnqw/edit#gid=429607552", sheet = 3, n_max = 21)

start_1 <- start_1 %>% janitor::clean_names()
start_2 <- start_2 %>% janitor::clean_names()
start_3 <- start_3 %>% janitor::clean_names()

end_1 <- end_1 %>% janitor::clean_names()
end_2 <- end_2 %>% janitor::clean_names()
end_3 <- end_3 %>% janitor::clean_names()

```

## pseudonyms (not printed)

```{r, echo = FALSE}
pseudonyms <- c(
  "Jaime Olaya" = "Jordan",
  "Evan Chen" = "Liam",
  "Hazel Jamtsho" = "Grace",
  "Colin Chen" = "Aiden",
  "Amberamora Edwards" = "Sophia",
  "Jacqueline Dutan" = "Isabella",
  "Davien Martinez" = "Michael",
  "Ellianne Torivio" = "Olivia",
  "Andy Lu" = "Lucas",
  "Rex He" = "Jack",
  "Samantha Peralta" = "Emma",
  "Ariana Rojas" = "Mia",
  "Esteban Ortiz" = "Noah",
  "Sophie Zhang" = "Ava",
  "Dominic Del Rosario" = "Ethan",
  "Ryan Berrios" = "James",
  "America Cuevas" = "Charlotte",
  "Alan Chen" = "Benjamin",
  "Pablo" = "Henry"
)

pseudonyms["Pablo Cunache"] <- "Henry" # for a small difference
```

```{r}
start_1 <- start_1 %>% rename(names = to_start_please_enter_your_first_and_last_name_below)

start_1 <- start_1 %>% mutate(names = tools::toTitleCase(names))

start_1 <- start_1 %>%
  mutate(names = recode(names,
                        !!!pseudonyms
  ))
```

## Campers (n's at diff. time points)

pre
- 1
- 2
- 3

post 
- 1 
- 2
- 3

## Start of Camp Descriptives

### Framing

```{r}

#| fig-cap: "Start of camp, framing"

start_1 <- start_1 %>% 
  mutate(when_was_the_pokemon_game_first_created = recode(when_was_the_pokemon_game_first_created,
                                                          "I could use or collect a data set to answer this question." = -1,
                                                          "I could answer the question without data." = 1,
                                                          "I'm not sure." = 0,
                                                          .default = 0
  ))

start_1 <- start_1 %>% 
  mutate(what_do_kids_learn_by_playing_pokemon_games = recode(what_do_kids_learn_by_playing_pokemon_games,
                                                              "I could use or collect a data set to answer this question." = 1,
                                                              "I could answer the question without data." = -1,
                                                              "I'm not sure." = 1,
                                                              .default = 0
  ))

start_1 <- start_1 %>% 
  mutate(how_has_the_price_of_the_holographic_charizard_card_changed_since_it_first_came_out = recode(how_has_the_price_of_the_holographic_charizard_card_changed_since_it_first_came_out,
                                                                                                      "I could use or collect a data set to answer this question." = 1,
                                                                                                      "I could answer the question without data." = -1,
                                                                                                      "I'm not sure." = 1,
                                                                                                      .default = 0
  ))

start_1 <- start_1 %>% 
  mutate(is_pikachu_the_most_popular_pokemon = recode(is_pikachu_the_most_popular_pokemon,
                                                      "I could use or collect a data set to answer this question." = 1,
                                                      "I could answer the question without data." = -1,
                                                      "I'm not sure." = 1,
                                                      .default = 0
  ))

start_1 %>% select(when_was_the_pokemon_game_first_created:is_pikachu_the_most_popular_pokemon) %>% 
  gather(key, val) %>% 
  ggplot(aes(x = val)) + 
  geom_histogram() +
  facet_wrap(~key, nrow = 4) +
  theme_minimal() +
  labs(subtitle = "1 = I could use data; 0 = not sure; -1 = I could not use data")

```

### Collecting

```{r}

#| fig-cap: "Start of camp, collecting"
#| 
start_2 %>% 
select(approach_1_if_anyone_gets_sick_its_probably_not_safe:approach_4_place_an_air_quality_sensor_in_each_classroom) %>% 
  select(-approach_2_ask_the_first_200_students_who_arrive_at_school_if_anything_is_bothering_them) %>% 
  gather(key, val) %>% 
  mutate(key = str_sub(key, start = 1, end = 10)) %>% 
  mutate(key = recode(key,
                      "approach_1" = "anyone sick",
                      "approach_3" = "front door",
                      "approach_4" = "every class"
  )) %>% 
  ggplot(aes(x = key, y = val, fill = val)) +
  geom_col(position = "dodge") +
  scale_fill_viridis_d("") +
  theme_minimal()
```

### Visualizing

```{r}

#| fig-cap: "Start of camp, visualizing"

start_3 %>% 
  select(table = how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_table_above_4,
         bad_area = how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_chart_above_5,
         bar = how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_chart_above_6) %>% 
  mutate(bad_area = recode(bad_area, 
                           "1" = 5,
                           "2" = 5,
                           "3" = 3,
                           "4" = 2,
                           "5" = 1)) %>% 
  gather(key, val) %>% 
  ggplot(aes(x = val, fill = key)) +
  geom_histogram() +
  facet_wrap(~key) +
  theme_minimal() +
  scale_fill_viridis_d() +
  theme(legend.position = "none") +
  labs(subtitle = "Scale is from 1 (very hard) to 5 (very easy)",
       caption = "The first pane, bad_area is reverse-coded, such that the values of 5 were originally 'very hard', and 1 were 'very easy'")
```

## End of Camp Descriptives

### Framing

```{r}

#| fig-cap: "End of camp, framing"

end_1 <- end_1 %>% 
  slice(-c(1:5))

end_1 <- end_1 %>% rename(names = to_start_please_enter_your_first_and_last_name_below)

end_1 <- end_1 %>% mutate(names = tools::toTitleCase(names))


end_1 <- end_1 %>%
  mutate(names = recode(names,
                        !!!pseudonyms
  ))

end_1 <- end_1 %>% select(names, how_many_points_did_each_player_score_in_a_typical_game, who_is_the_team_mascot, which_player_was_the_best_defender_this_season) %>% 
  mutate(how_many_points_did_each_player_score_in_a_typical_game = recode(how_many_points_did_each_player_score_in_a_typical_game,
                                                                          "I could use data to answer this question." = 1,
                                                                          "I could answer the question without data." = -1,
                                                                          "I'm not sure." = 0,
                                                                          .default = 0
  ),
  who_is_the_team_mascot = recode(who_is_the_team_mascot,
                                  "I could use data to answer this question." = -1,
                                  "I could answer the question without data." = 1,
                                  "I'm not sure." = 0,
                                  .default = 0
  ),
  which_player_was_the_best_defender_this_season = recode(which_player_was_the_best_defender_this_season,
                                                          "I could use data to answer this question." = 1,
                                                          "I could answer the question without data." = -1,
                                                          "I'm not sure." = 0,
                                                          .default = 0
  ))


end_1 %>% 
  select(-names) %>% 
  gather(key, val) %>% 
  ggplot(aes(x = val)) + 
  geom_histogram() +
  facet_wrap(~key, nrow = 4) +
  theme_minimal()
```

### Collecting

```{r}

#| fig-cap: "End of camp, collecting"

end_2 <- end_2 %>% 
  slice(-c(1:6))

names(end_2)[7:9] <- str_c("q", 1:3)

# Example list
lst <- list(1, 2, NULL, 4, 5)

# Replace NULL with NA
end_2$q2 <- lapply(end_2$q2, function(x) if (is.null(x)) NA else x)
end_2$q3 <- lapply(end_2$q3, function(x) if (is.null(x)) NA else x)

end_2$q1 <- unlist(end_2$q1)
end_2$q2 <- unlist(end_2$q2)
end_2$q3 <- unlist(end_2$q3)

end_2 %>% 
  select(q1:q3) %>% 
  rename(anyone = q1, front_door = q2, each_class = q3) %>% 
  mutate_all(str_sub, end = 2) %>% 
  mutate_all(as.numeric) %>% 
  mutate(anyone = recode(anyone,
                         "1" = 3,
                         "3" = 1)) %>% 
  gather(key, val) %>% 
  ggplot(aes(x = val)) + 
  geom_histogram() +
  facet_wrap(~key, nrow = 4) +
  theme_minimal() +
  labs(caption = "1 = worst, 3 = best; 'anyone' reverse coded")
```

### Visualizing

```{r}

#| fig-cap: "End of camp, visualizing"

end_3 %>% 
  select(table = how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_table_above,
         bad_area = how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_chart_above_4,
         bar = how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_chart_above_5) %>% 
  mutate(bad_area = recode(bad_area, 
                           "1" = 5,
                           "2" = 5,
                           "3" = 3,
                           "4" = 2,
                           "5" = 1)) %>% 
  gather(key, val) %>% 
  ggplot(aes(x = val, fill = key)) +
  geom_histogram() +
  facet_wrap(~key) +
  theme_minimal() +
  scale_fill_viridis_d() +
  theme(legend.position = "none") +
  labs(subtitle = "Scale is from 1 (very hard) to 5 (very easy)",
       caption = "The first pane, bad_area is reverse-coded, such that the values of 5 were originally 'very hard', and 1 were 'very easy'")
```

## Pre-Post

### Framing

```{r}
#| fig-cap: "Pre-post change, framing"
#| 
start_1_means <- start_1 %>% select(names, when_was_the_pokemon_game_first_created:is_pikachu_the_most_popular_pokemon) %>% 
gather(key, val, -names) %>% 
  group_by(names) %>% 
  summarize(mean_score_start = mean(val, na.rm = TRUE))

end_1_means <- end_1 %>% 
  gather(key, val, -names) %>% 
  group_by(names) %>% 
  summarize(mean_score_end = mean(val, na.rm = TRUE))

start_1_means %>% 
  left_join(end_1_means) %>% 
  gather(key, val, -names) %>% 
  mutate(key = recode(key,
                      "mean_score_start" = "beginning",
                      "mean_score_end" = "end")) %>% 
  ggplot(aes(x = key, y = val, group = names, color = names)) +
  geom_point() +
  geom_line() +
  theme_minimal() +
  facet_wrap(~names)

start_1_means %>% 
  left_join(end_1_means) %>% 
  gather(key, val, -names) %>% 
  mutate(key = recode(key,
                      "mean_score_start" = 1,
                      "mean_score_end" = 2)) %>% 
  ggplot(aes(x = key, y = val)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point() + 
  theme_minimal() +
  ylab("Mean Score (-1 - 1)")
```

### Gathering (not examined)

```{r}
start_2 <- start_2 %>% rename(names = please_enter_your_name_or_nickname)

start_2 <- start_2 %>% mutate(names = tools::toTitleCase(names))

```

```{r, echo = FALSE}
# Create a named vector for pseudonyms
pseudonyms_two <- c(
  "Colin Chen" = "Alex Smith", 
  "Gamer" = "Jamie Brown", 
  "Evan Chen" = "Taylor Johnson", 
  "Hazel" = "Casey Lee", 
  "Rex Hee" = "Jordan White", 
  "Jacquie" = "Morgan Green", 
  "Davien Martinez" = "Avery Hall", 
  "Amberamora (Pronounced: Amber-Amora)" = "Riley Adams", 
  "Sophie" = "Charlie Davis", 
  "Ryan Berrios" = "Peyton Clark", 
  "Andy Lu" = "Cameron Lewis", 
  "Ellianne Torivio" = "Quinn Walker", 
  "Ariana" = "Reese Robinson", 
  "Sam" = "Harper King", 
  "Alan Chen" = "Dylan Wright", 
  "Dominic" = "Rowan Scott", 
  "Esteban Ortiz" = "Hayden Morgan",
  "Amberamora Edwards" = "Riley Adams",
  "Ariana Rojas" = "Reese Robinson",
  "Hazel Jamtsho" = "Casey Lee",
  "Samantha" = "Harper King",
  "Andy" = "Cameron Lewis",
  "EllianneTorivio" = "Quinn Walker",
  "Rex" = "Jordan White",
  "Pablo" = "Blake Harris",
  "America" = "Skyler Thompson"
)
```

```{r}
end_2 <- end_2 %>% rename(names = please_enter_your_name_or_nickname)

end_2 <- end_2 %>% mutate(names = tools::toTitleCase(names))
```

```{r}
start_2 <- start_2 %>%
  mutate(names = recode(names,
                        !!!pseudonyms_two
  ))

end_2 <- end_2 %>%
  mutate(names = recode(names,
                        !!!pseudonyms_two
  ))
```

### Visualizing

```{r}
start_3_sub <- start_3 %>% select(names = please_enter_your_name_or_nickname,
                   how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_table_above_3,
                   how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_table_above_4,
                   how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_chart_above_5,
                   how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_chart_above_6)

# Create pseudonyms
start_3_sub <- start_3_sub %>%
  mutate(pseudonym = case_when(
    names == "Colin Chen" ~ "Colin",
    names == "Ariana" ~ "Ariana Rojas",
    TRUE ~ names
  ))


end_3_sub <- end_3 %>% select(names = please_enter_your_name_or_nickname,
                 how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_table_above,
                 how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_chart_above_4,
                 how_hard_would_it_be_to_find_the_month_with_the_most_birthdays_using_the_chart_above_5)

# start_3_sub$names %>% clipr::write_clip()
# end_3_sub$names %>% clipr::write_clip()
```
